%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Notes on Citations
%
% MooreAfter2017.bib is an export of the MooreAfter2017 saved search in my Zotero database.
%
% Make sure that the citekey is pinned to each item ( Right click; Better Bibtex | Pin Bibtex key)
%
% After uploading, click on Tools | Bibliography, then open the log file to see any warnings
% or errors which need to be fixed. 
%
% Fix any problems in Zotero, then export a fresh version of MooreAfter2017.bib
%
% Keywords in the MooreAfter2017.bib are used as filters. Note that keywords
% cannot contain space characters.
% 
% Example:
% \begin{refsection}
%	\nocite{*}
%	\printbibliography[heading=none, keyword={Moore-presentations-after-2017}]
% \end{refsection} 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Checking links in PDF
%
% pdfx -c CFES2019.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Subsection format
%
% \begin{refsection}
% \subsubsection{Description}
% \subsubsection{Activities}
% \subsubsection{Plans}
% \subsubsection{References}
% \printbibliography[heading=none]
% \end{refsection}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,english,letterpaper]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{array}
\usepackage{url}
\usepackage{pdfpages}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}

% Use style=draft to print citation keys
%\usepackage[defernumbers=true,backend=biber,style=draft]{biblatex}
\usepackage[defernumbers=true, backend=biber, sorting=none]{biblatex}

\addbibresource{addendum-mylibrary.bib}
\addbibresource{addendum-CRB.bib}
\usepackage[breaklinks=true, colorlinks=True, allcolors=blue]{hyperref}

\usepackage{indentfirst} 
\usepackage{comment}

% A couple of very simple macros to add 'Activities' and 'Plans' headings.
\newcommand{\activities}{\medskip\textbf{Activities}}
\newcommand{\plans}{\medskip\textbf{Plans}}

\makeatletter

\makeatother

\errorcontextlines=3 % For checking biblatex

\begin{document}

\title{Addendum to CFES Report 2019\\ \large{Activity between February 17, 2020 and June 15, 2020}}

\author{Aubrey Moore, Ph.D.\\
Professor / Extension Entomologist}

\maketitle

\textbf{Note to Reader:}

This report is available as an electronic document in PDF format at\\
\url{https://github.com/aubreymoore/CFES2019-addendum/blob/master/CFES2019-addendum.pdf}

If you are reading the PDF version of the report on a device connected
to the internet, you will be able to follow hypertext links to documents
I have referenced.

\setcounter{tocdepth}{2}
\tableofcontents{}

\clearpage

\section{Grant Proposals Prepared and Submitted (n=3)}
\begin{refsection}

I prepared and submitted three grant proposals: one submitted to the Department of Defense Strategic Environmental Research and Development Program (SERDP) requesting \$3.6M \cite{moore_serdp_2020-1} and two submitted to the US Forest Service requesting \$240K and \$23K \cite{moore_grant_2020-1, moore_grant_2020}.	

\printbibliography[heading=none]
\end{refsection} 


\section{Grant Reports Prepared and Submitted (n=3)}
\begin{refsection}
\nocite{moore_progress_2020, moore_progress_2020-2, moore_progress_2020-1}
\printbibliography[heading=none]
\end{refsection}

\newpage

\section{Technical Reports (n=3)}
\begin{refsection}
\nocite{grasela_technical_2020, grasela_technical_2020-1, grasela_technical_2020-2}
\printbibliography[heading=none]
\end{refsection}


\section{Journal Articles in Preparation (n=7)}
\begin{refsection}
\nocite{moore_first_nodate-1,moore_mariana_2013,moore_three_nodate-1,moore_change_nodate,moore_aubrey_crb_nodate,marshall_recent_nodate,moore_coconut_nodate-1}
\printbibliography[heading=none]
\end{refsection}

\newpage
	
\section{Miscellaneous Activities}
\begin{refsection}

\begin{description}
	\item[Head Start] On 2020-02-28 I lead a mini-workshop for 3 groups of the Guam Head Start Program participants.
	
	\item[UOG Charter Day] On 2020-03-10 I set up and manned a display about Guam's insects.
	 
	\item[GISC] On 2020-02-22 I represented the University at the Guam Invasive Species Council.
		
	\item[Journal Article Review] I reviewed a draft journal article entitled \textit{Coconut Rhinoceros Beetle unpredictably adds Guam cycads to its host range}.
	
	\item[Zoom conferences] I set up weekly Zoom conferences for the Agriculture and Natural Resources Program.
	
	\item[Eight-spot Butterfly Conservation] I partially installed a large field cage (20ft x 20ft x 10 ft) in the Center for Island Sustainability Center compound in Dean's Circle. Work on this project has been interrupted by COVID-19.
	
	\item[Selection Committees] I served on 3 selection committees for RCUOG employees.
	
	\item[COVID-19] I was invited to participate in an \textit{ad hoc} group interested in modeling the COVID-19 outbreak on Guam.
	I participated in an online Zoom session with the group, published a Medium article entitled \textit{Fitting Curves to COVID-19 Data for Guam and Hawaii} \cite{moore_fitting_2020}, and published Jupyter Notebooks which facilitate access to and visualization of timeseries for Guam COVID-19 data \cite{moore_github_2020}. I also reviewed a draft article entitled \textit{Proposal for Immediate Infection Mitigation and Long Term Suppression Measures Aimed at Economic Revitalization and Discontinuing Physical Distancing}.
		
\end{description}
\printbibliography[heading=none]
\end{refsection}


\end{document}
